---
title: "ggplot Tutorial"
author: "[Yung Chou](http://yungchou.wordpress.com/)"
output:
html_document: default
word_document: default
pdf_document: default
---

[Visualization ggplot2](https://www.pinterest.com/nomisroth/visualization-ggplot2/)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
First, install the package and load it into the library. And this tutorial uses the mpg dataset included in ggplot2.

```{r}

#install.packages('ggplot2')
library(ggplot2)

# RStudio built-in sample file
head(mpg)
```

Set the default of a plot. Here, the data source is the mpg dataset, while specifying ***displ*** as the x axis and ***hwy*** as the y. This action sets the default of and does not produce a plot yet.

```{r}
# Set default
g <- ggplot(data = mpg, aes(x = displ, y = hwy))

```
To produce a plot, need to provide the default to layers called  [***geoms***](https://ggplot2.tidyverse.org/reference/#section-layer-geoms) usng '**+**' which works just list piping, **%>%**, in **dplyr**. For example, **geom_point** is to create a scatterplot.

```{r}
g + geom_point() 
```

And use **theme** to customize a plot.
```{r}
g + geom_point(aes(col=cty, size=displ)) + 
  labs(
    title="MPG vs. Engine Displcement", 
    x="Displacement", 
    y="Highway MPG", 
    caption="Source: ggplot sample file") +
  theme(
    plot.title=element_text(
      size=20, 
      face="bold", 
      family="Sego UI Light", 
      color="Blue", 
      hjust=0.5, 
      lineheight=1.2), 
    plot.subtitle=element_text(
      size=11, 
      family="Sego UI Light", 
      face="bold", 
      hjust=0.5),
    plot.caption=element_text(size=11),
    axis.title.x=element_text(size=11, vjust=0),
    axis.title.y=element_text(size=11),
    axis.text.x=element_text(size=11, angle = 0, vjust=.5),
    axis.text.y=element_text(size=11))

```

```{r}
#library(ggplot2)
head(diamonds)

g <- ggplot(diamonds, aes(x=carat, y=price))

# With individual colors of smooth lines
g + geom_point(aes(x=carat, y=price, color=cut)) +
  geom_smooth(aes(x=carat, y=price, color=cut))    

# With one smooth line for all data
g + geom_point(aes(x=carat, y=price, color=cut)) +
  geom_smooth(aes(x=carat, y=price))

ggplot(diamonds, aes(x=carat, y=price, color=cut, shape=color)) +
  geom_point()

head(mpg)

g <- ggplot(mpg, aes(x=manufacturer, y=hwy))

g + geom_point()
g + geom_point() + geom_jitter()
```


```{r}
g + geom_point() + geom_smooth(method = "lm")

```

```{r}
g + geom_point(aes(color = class))
g + geom_point(aes(size = class))
g + geom_point(aes(shape = class))
g + geom_point(aes(alpha = class))
```



```{r}
g + geom_point() + facet_grid(. ~ cyl)
g + geom_point() + facet_grid(drv ~ .)
g + geom_point() + facet_grid(drv ~ cyl)
g + geom_point() + facet_wrap( ~ class)

```

Now use the diamonds dataset included in ggplot2.
```{r}
ggplot(data = diamonds, aes(x = cut)) + geom_bar(aes(fill = cut))
ggplot(data = diamonds, aes(x = color)) + geom_bar(aes(fill = cut))
```

```{r}
g <- ggplot(data = diamonds, aes(x = depth))
zoom <- coord_cartesian(xlim = c(55, 70))
g + geom_histogram(binwidth = 0.2) + zoom

```

```{r}
g + geom_histogram(aes(fill=cut), binwidth = 0.2,
                   position = position_stack(reverse=TRUE)) + zoom

```

```{r}
g + geom_histogram(binwidth = 0.2) + facet_wrap( ~ cut) + zoom

```

```{r}
g + geom_histogram(binwidth = 0.2) + geom_freqpoly(binwidth=0.2) + facet_wrap( ~ cut) + zoom

```

```{r}
g + geom_freqpoly(aes(color = cut), binwidth = 0.2) + facet_wrap( ~ cut) + zoom

```

```{r}
g + geom_freqpoly(aes(color = cut), binwidth = 0.2) + zoom

```

```{r}
g <- ggplot(data = diamonds, aes(x = carat, y = price))
g + geom_point(aes(color = cut))

```

```{r}
g + geom_point() + geom_density2d()
g + geom_point() + geom_smooth(aes(color = cut), method = "loess", se = FALSE)
g + geom_point(size = 0.5, alpha=0.05)

```

